Computer Science House By-Laws

### 2016-11-07 bylaws.tex
Added Simple Majority specification to Evals votes
Fixes #27

	\item The application materials are then reviewed at an Evaluations meeting and the members present vote on whether to accept the person as an introductory member.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
	This may occur only once per Introductory Evaluation Process.
\end{enumerate}

>>>>

	\item The application materials are then reviewed at an Evaluations meeting. 
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an introductory member.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
